ScipionBox: automatic processing for

### 2017-06-07 introduction.tex
small changes previous to first public release

3D electron microscopy (3DEM)  can provide rich information about structural characteristics of macromolecular complexes. The field is under a major transformation due to the arrival of better microscopes [**REF], new large area detectors [**REFS ddd] and automatization [**REFs to data colection software as EPU, leginon, serialEm,etc...]  which makes possible that a single microscope generates high quality data sets on the order of terabytes per day [**REF] while working for several days without interruption. Major challenges faced in the field are: (1) an efficient management of these huge datasets and their corresponding image processing workflows; (2) a raising interest from scientists outside the field who might lack the skills of experienced microscopist and; (3) an the need for an effective transference of data and associated metadata in an increasingly distributed and collaborative environment. This situation places techniques that are automated and allow higher throughput in high demand.

@@

Many software packages have been developed to provide automated data collection, such as SerialEM (Mastronarde, 2005), Leginon (Suloway et al., 2005), UCSF-Tomography (Zheng et al., 2007), Tom Toolbox (Nickell et al.2005), EPU (Thermo Fisher Co.), Latitude in Digital Micrograph (Gatan Co.), or EMMenu
(TVIPS, Germany), etc. However, the next step,  which is to provide image processing while  data are being collected, is not so well served. In fact, in most places this is accomplished through home made scripts. Exceptions are UCSFImage4 [**REF] and Focus (Biayi et al 2017). As we will explain here, \scipionbox differs from these solutions in a larger flexibility both from the point of view of users and facility staff.  [**this parragraph need to be improved]

>>>>

3D electron microscopy (3DEM)  can provide rich information about structural characteristics of macromolecular complexes. The field is under a major transformation due to the arrival of better microscopes [**REF], new large area detectors [**REFS ddd] and automatization [**REFs to data colection software as EPU, leginon, serialEm,etc...]  which makes possible that a single microscope generates high quality data sets on the order of terabytes per day [**REF] while working for several days without interruption. Major challenges faced in the field are: (1) an efficient management of these huge datasets and their corresponding image processing workflows; (2) a raising interest from scientists outside the field who might lack the skills of experienced microscopist and; (3) the need for an effective transference of data and associated metadata in an increasingly distributed and collaborative environment. This situation places techniques that are automated and allow higher throughput in high demand.

@@

Many software packages have been developed to provide automated data collection, such as SerialEM (Mastronarde, 2005), Leginon (Suloway et al., 2005), UCSF-Tomography (Zheng et al., 2007), Tom Toolbox (Nickell et al.2005), EPU (Thermo Fisher Co.), Latitude in Digital Micrograph (Gatan Co.), or EMMenu
(TVIPS, Germany), etc. However, the next step,  which is to provide image processing while  data are being collected, is not so well served. In fact, in most places this is accomplished through home made scripts. Exceptions are UCSFImage4 [**REF] and Focus (Biayi et al 2017). As we will explain here, \scipionbox differs from these solutions in a larger flexibility both from the point of view of users and facility staff.
